MATH 3610 - Project \#1

### 2015-10-01 proj1.tex
Adding justifications of gamma

In the preceding model, once people became infected, they stayed
	infected for the duration of the run.
The following model adds a parameter, the ``curing rate'' $\gamma$,
	which represents the rate at which individuals in the sick population
	recover (and join the removed population).
This model is the SIR model, and has standard parameters:

@@

\subsection{Disease Spread between Coupled Populations}

Consider three populations, with two connected only by an intermediate
	one.

\begin{align*}
\frac{d\widetilde{I}_1}{dt} & = \left( \left( r_{11} K_1 \right) \widetilde{I}_1 
			+ \left( r_{12} K_2 \right)  \widetilde{I}_2 \right)
		\left( 1 - \widetilde{I}_1 - \left( \frac{\alpha_1}{K_1} \right) t \right)\\
\frac{d\widetilde{I}_2}{dt} & = \left( \left( r_{22} K_2 \right) \widetilde{I}_2 
			+ \left( r_{21} K_1 \right)  \widetilde{I}_1 
			+ \left( r_{23} K_3 \right) \widetilde{I}_3 \right)
		\left( 1 - \widetilde{I}_2 - \left( \frac{\alpha_2}{K_2} \right) t \right)\\
\frac{d\widetilde{I}_3}{dt} & = \left( \left( r_{33} K_3 \right) \widetilde{I}_3 
			+ \left( r_{32} K_2 \right)  \widetilde{I}_2 \right)
		\left( 1 - \widetilde{I}_3 - \left( \frac{\alpha_3}{K_3} \right) t \right)
\end{align*}

If the second population is relatively small, then we might be able to 
	decrease the total number of infections by focusing our entire efforts
	on the smallest population to cut the link between the two populations.
We then treat the vaccination problem as a pareto optimization problem, to distribute
	the vaccines amongst the two populations.
However this may not be better than splitting the vaccinations between the two.

>>>>

In the preceding model, once people became infected, they stayed
	infected for the duration of the run.
The following model adds a parameter, the ``curing rate'' $\gamma$,
	which represents the rate at which individuals in the sick population
	recover (and join the removed population).
This will be the inverse of the time spent sick, which is on average 
	1 week \cite{CIC-stats}.
The value of the interaction parameter $\beta$ is determined in \textbf{PLACEHOLDER}
This model is the SIR model, and has standard parameters:

@@

\subsection{Coupling the Populations}

Consider the following modifications to the model, to add interactions.
Let $\alpha$ be the interaction coefficient.
$\alpha$ should be approximately a fraction of $\beta$.
For example, if a member of one population is one tenth as likely
	to interact with the other as with one from their own population,
	the value for $\alpha$ would be $\frac{\beta}{10}$.
It represents how likely the seceptible of $i$ are to be infected by the
	infected of $j$.

\begin{align*}
\frac{dI_1}{dt} & = \frac{ \beta S_1 I_1}{N_1} + \frac{ \alpha S_1 I_2 }{N_2} - \gamma I_1\\
\frac{dS_1}{dt} & = -\frac{\beta S_1 I_1}{N_1}  - \frac{ \alpha S_1 I_2 }{N_2} - r_v \\
\frac{dR_1}{dt} & = r_v + \gamma I_1 \\
\frac{dI_2}{dt} & = \frac{ \beta S_2 I_2}{N}  + \frac{ \alpha S_2 I_1 }{N_1} - \gamma I_2\\
\frac{dS_2}{dt} & = -\frac{\beta S_2 I_2}{N}  - \frac{ \alpha S_2 I_1 }{N_1} - r_v \\
\frac{dR_2}{dt} & = r_v + \gamma I_2 
\end{align*}

This model, in the fully interacting case, produces the following pareto curve:

\includegraphics[width=0.5\textwidth]{figures/sir-interacting.pdf}

This doesn't show a significant variance across different immunization strategies.
It seems like vaccinating one population, and then the other, is a reasonable
	immunization strategy.
If we want to be in the middle, that is alright.
